### 2016-09-14 NOEMA/Proposal16/RXJ.tex
prob. more conservative to say A array only is 0.4

\vspace{.2em}
\noindent {\bf Technical justification} 
% A+C: ~0.66" at 209 GHz
We propose to observe \cco emission in RXJ1131 at $z_{\rm CO}$\eq0.6537 at the 
redshifted line frequency of 209.10443\,GHz ($\nu_{\rm rest}$\eq345.79599\,GHz) using the A+C array configurations. 
Given the spatial extent the quasar host galaxy ($\sim$3.8'' in diameter), 
we request C-array \obs to provide short spacings 
to maximize the sensitivity and $uv$ coverage for lens modelling, and to
ensure that diffuse lensed emission on $\gtrsim$0.3'' scale is not resolved out. % just A array
% To maximize the sensitivity and UV coverage of the maps and to ensure that no flux was resolved out at the highest resolution, we combined the extended configuration data with the compact configuration observations. 
We estimate the expected source size based on the
most extended kinematic component in our dynamical lens model of the \bco data, which takes into account the asymmetric line emission and spatial extent across different velocity bins (arising due to differential lensing).
We therefore expect the source to be resolved over $\sim$10 beams at the proposed angular resolution of $\sim$0.66''.
We compute the expected \cco line strength based on our 
CARMA \cco line flux of $I$\eq35.7\,Jy\,\kms and line FWHM of $\sim$700\,\kms.
To obtain sufficient S/N for dynamical lens modelling over 7$-$10 velocity bins, 
we require a 10$\sigma$ detection of $\sigma$\eq1.35\,mJy\,beam\pmOne per 100\,\kms bin,
{\bf requiring only $\sim$1.5 hours on source} (and 2.4 hours including overheads) with 8 antennas.
We note that the requested sensitivity will correspond to S/N$>$10 for channels with spatially less extended emission, which are also found to have lower magnification factors (and thus lower apparent flux density).

>>>>

\vspace{.2em}
\noindent {\bf Technical justification} 
% A+C: ~0.66" at 209 GHz
We propose to observe \cco emission in RXJ1131 at $z_{\rm CO}$\eq0.6537 at the 
redshifted line frequency of 209.10443\,GHz ($\nu_{\rm rest}$\eq345.79599\,GHz) using the A+C array configurations. 
Given the spatial extent the quasar host galaxy ($\sim$3.8'' in diameter), 
we request C-array \obs to provide short spacings 
to maximize the sensitivity and $uv$ coverage for lens modelling, and to
ensure that diffuse lensed emission on $\gtrsim$0.4'' scale is not resolved out. % just A array
% To maximize the sensitivity and UV coverage of the maps and to ensure that no flux was resolved out at the highest resolution, we combined the extended configuration data with the compact configuration observations. 
We estimate the expected source size based on the
most extended kinematic component in our dynamical lens model of the \bco data, which takes into account the asymmetric line emission and spatial extent across different velocity bins (arising due to differential lensing).
We therefore expect the source to be resolved over $\sim$10 beams at the proposed angular resolution of $\sim$0.66''.
We compute the expected \cco line strength based on our 
CARMA \cco line flux of $I$\eq35.7\,Jy\,\kms and line FWHM of $\sim$700\,\kms.
To obtain sufficient S/N for dynamical lens modelling over 7$-$10 velocity bins, 
we require a 10$\sigma$ detection of $\sigma$\eq1.35\,mJy\,beam\pmOne per 100\,\kms bin,
{\bf requiring only $\sim$1.5 hours on source} (and 2.4 hours including overheads) with 8 antennas.
We note that the requested sensitivity will correspond to S/N$>$10 for channels with spatially less extended emission, which are also found to have lower magnification factors (and thus lower apparent flux density).
